### 2019-01-13 papers/journal/related.tex
restructure introduction and started experiments section. Added references to the bio part of the intro section.
Table update

SAT and SMT solvers are a perfect fit for solving combinatorial problems due to their exhaustive nature of searching. 
%
Improvement in SAT and SMT solvers in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules with possible exhaustive search and hence can be reduced to solving a SAT/SMT question. 
%
Modeling and understanding the gene regulatory networks (GNR)~\cite{guerra2012reasoning,chin2008biographe}, modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis} is one such example. 
%
We have extended the application of SAT and SMT solvers to the most comple Biological transport network (VTS)~\cite{mani2016stacking,shukla}.

>>>>

Previous analysis of vesicle traffic system has used simulation and statistical reasoning~\cite{mani2016stacking}. 
%
Such analysis is far from complete and can only make statistical claims based on a subset of samples. 
%
The properties of VTS required precise analysis for all possible rules and variations that make formal methods a suitable choice.

The Boolean satisfiabilty (SAT) solvers are used to solve wide range of problems including
%
software and hardware verification, equivalence checking, automatic test generation,
AI planning, scheduling and program synthesis. 
%
The enormous progress in the performance of SAT and SMT solvers
%Improvement in SAT and SMT solvers
in the past decades have led to their use in modeling and understanding complex biological systems~\cite{heule2010exact,yordanov2013smt,mangla2010timing}. 
%
Many of which involve reasoning about graphs and networks rules~\cite{guerra2012reasoning,chin2008biographe} with possible exhaustive search.
% and hence can be reduced to solving a SAT/SMT question. 
%

One of the prominent areas of application of SAt/SMT solvers are modeling and understanding the gene regulatory networks (GNR)~\cite{giacobbe2015model,rosenblueth2014inference, batt2010efficient, yordanov2016method, dunn2014defining, paoletti2014analyzing, koksal2013synthesis}.
%
We have extended the application of SAT and SMT solvers to the most complex Biological transport network (VTS)~\cite{mani2016stacking,shukla}.
